Weakly Nonlinear MRI: Notes

### 2014-04-01 notes/mri_notes.tex
more details fille in
explanation of second amplitude equation

@@

$\mathcal{D} \mathbb{V}_{11} e^{iQz}\partial_T \alpha \, + \, \alpha \left| \alpha^2 \right| \mathbf{N}_{31} e^{iQz} \, + \, \alpha \partial_Z \beta \widetilde{\mathbf{N}}_{31} e^{iQz} \, = \, - \partial_Z^2 \alpha \widetilde{\mathcal{L}}_1 \mathbb{V}_{21} e^{iQz} \, + \, \partial_Z^2 \alpha \widetilde{\mathcal{L}}_2 \mathbb{V}_{11} e^{iQz} \, - \, \partial_Z \alpha \mathbb{V}_{11}\mathcal{X}e^{iQz} \, - \, iQ^3 \alpha \mathcal{L}_3 \mathbb{V}_{11} e^{iQz}$ \\

@@

$a \partial_T \alpha \, + \, c \alpha \left|\alpha^2\right| \, + \, \widetilde{c} \alpha \partial_Z \beta \, = \, - b \partial_Z \alpha \, + \, h \partial_Z^2 \alpha \, - \, g i Q^3 \alpha$ \\

@@

>>>>

Which, substituting in the forms of $\mathbf{V_1}$ and $\mathbf{V_2}$ and taking Umurhan+'s $\mathbf{N3}$, gives us the full amplitude equation:\\

$\mathcal{D}\mathbb{V}_{11} e^{iQz}\partial_T \alpha \, + \, \mathcal{D}\mathbb{U}_{11} \partial_T \beta \, + \, \alpha^3 \mathbf{N_{33}} e^{i3Qz} \, + \, \alpha \partial_Z \alpha \mathbf{N_{32}} e^{i2Qz} \, + \, \alpha\left|\alpha\right|^2 \mathbf{N_{31}} e^{iQz} \, + \, \alpha \partial_Z\beta \widetilde{\mathbf{N}}_{31} e^{iQz} \, + \, \alpha^* \partial_Z \alpha \mathbf{N_{30}} \, = \, \mathcal{L}\mathbf{V_3} \, + \, \widetilde{\mathcal{L}}_1 \mathbb{V}_{22} 2 \alpha \partial_Z \alpha e^{i2Qz} \, + \, \widetilde{\mathcal{L}}_1 \mathbb{V}_{20} 2 \left|\alpha\right| \partial_Z \alpha \, - \, \widetilde{\mathcal{L}}_1 \mathbb{V}_{21} \partial_Z^2 \alpha e^{iQz} \, - \, \widetilde{\mathcal{L}}_1 \mathbb{U}_{20} \partial_Z^2 \beta \, + \, \widetilde{\mathcal{L}}_2 \mathbb{V}_{11} e^{iQz} \partial_Z^2 \alpha \, + \, \widetilde{\mathcal{L}}_2 \mathbb{U}_{11} \partial_Z^2 \beta \, - \, \mathcal{X}\mathbb{V}_{11} e^{iQz} \partial_Z \alpha \, - \, \mathcal{X} \mathbb{U}_{11} \partial_Z \beta \, + \, \mathcal{L}_3 \mathbb{V}_{11} e^{iQz} iQ^3 \alpha $\\

@@

$\mathcal{D} \mathbb{V}_{11} e^{iQz}\partial_T \alpha \, + \, \alpha \left| \alpha^2 \right| \mathbf{N}_{31} e^{iQz} \, + \, \alpha \partial_Z \beta \widetilde{\mathbf{N}}_{31} e^{iQz} \, = \, - \partial_Z^2 \alpha \widetilde{\mathcal{L}}_1 \mathbb{V}_{21} e^{iQz} \, + \, \partial_Z^2 \alpha \widetilde{\mathcal{L}}_2 \mathbb{V}_{11} e^{iQz} \, - \, \partial_Z \alpha \mathbb{V}_{11}\mathcal{X}e^{iQz} \, + \, iQ^3 \alpha \mathcal{L}_3 \mathbb{V}_{11} e^{iQz}$ \\

@@

$a \partial_T \alpha \, + \, c \alpha \left|\alpha^2\right| \, + \, \widetilde{c} \alpha \partial_Z \beta \, = \, - b \partial_Z \alpha \, + \, h \partial_Z^2 \alpha \, + \, g i Q^3 \alpha$ \\

@@

There should be a second amplitude equation, found by taking all of the terms which have no z-dependence. These terms are: \\

$\mathcal{D}\mathbb{U}_{11} \partial_T \beta \, = \, \mathcal{L}\mathbf{V_3} \, + \, \widetilde{\mathcal{L}}_1 \mathbb{V}_{20} 2 \left|\alpha\right| \partial_Z \alpha \, - \, \widetilde{\mathcal{L}}_1 \mathbb{U}_{20} \partial_Z^2 \beta \, + \, \widetilde{\mathcal{L}}_2 \mathbb{U}_{11} \partial_Z^2 \beta \, - \, \mathcal{X} \mathbb{U}_{11} \partial_Z \beta \, $\\

And for the (B)-component of that equation, I find: \\

$\partial_T \beta \, = \, -\widetilde{u}_{20} \partial_Z^2 \beta \, + \, \frac{1}{\reym} \partial_Z^2 \beta \, - \, \alpha^* \partial_Z \alpha N_{30}^{(B)} \, + \, 2 \left|\alpha\right| \partial_Z \left| \alpha \right| \left(u_{20} \, - \, q\Omega_0A_{20}\right) \, + \, \frac{1}{\reym} \partial_x^2 B_{30} \, + \, \frac{1}{\reym} \partial_z^2 B_{30}$ \\

The fourth term on the RHS, which couples to the shear, does not appear in Umurhan+, and we need to investigate whether something in the lower-order solvability criterions allow this term to drop out. \\
